\title{Adaptive Control of a Generic Hypersonic Vehicle}
\author{Daniel Philip Wiese}
\prevdegrees{B.S. University of California, Davis (2011)}
\department{Department of Mechanical Engineering}
\degree{Master of Science}
\degreemonth{June}
\degreeyear{2013}
\thesisdate{May 10, 2013}
\supervisor{Anuradha M. Annaswamy}{Senior Research Scientist}
\chairman{David E. Hardt}{Chairman, Department Committee on Graduate Students}
\maketitle

\cleardoublepage%
\setcounter{savepage}{\thepage}
\begin{abstractpage}
\input{./chapters/abstract}
\end{abstractpage}

\cleardoublepage%

\section*{Acknowledgments}

I would like to thank my advisor Dr.\ Anuradha Annaswamy for her guidance during this research.
I would also like to thank Dr.\ Jonathan Muse and Dr.\ Michael Bolender in the Aerospace Systems Directorate at the Air Force Research Laboratory for providing the vehicle model for this research, giving their support and advice along the way, and providing direction during my summer work at AFRL.\@
Thanks to Dr.\ Eugene Lavretsky of Boeing Research \& Technology for contributing his invaluable advice and suggestions throughout this project.
Thanks also to all of my lab mates for our discussions and help through various research problems, and making lab enjoyable.
Their assistance and friendship over the last two years has been great.
I also want to thank Dr.\ Lutz, without whom I would not be where I am today.
I want to thank her for all of the encouragement and inspiration over the past five years, and for being a truly outstanding mentor.
Thanks as well to Bob for providing advice and wisdom.
I would like to thank all of my friends for their patience and understanding.
Finally, I would like to thank my Mom, Dad, and all of my family for their love and support all these years.

This research is funded by the Air Force Research Laboratory/Aerospace Systems Directorate grant FA 8650--07--2--3744 for the Michigan/AFRL Collaborative Center in Control Sciences, with Dr.\ Michael Bolender as technical monitor.
